\documentclass[11pt]{article}
\usepackage{multirow}


\begin{document}

\title{Test Plan}
\author{Kirk Montour\\ \and Syed Gardezi}


\date{\vspace{-5ex}}

\maketitle
\vspace{5 mm}

\textbf{\Large Functional Requirements Testing}

\vspace{5 mm}

\textbf{Front Controller Subsystem Test Plan :}

\begin{itemize}
\item Test front controller with home page request.
\item Test front controller with a secondary page request.
\item Test front controller with no page name and observe if it defaults to the home page.
\item Test front controller with a page name that doesn’t exist and observe if error page displays.
\end{itemize}

\vspace{2 mm}
\textbf{Login Subsystem Test Plan :}

\begin{itemize}
\item Test access to the administration area for non-authorized users, non-authorized users should be presented with a login page.
\item Test whether valid login redirects to Page Management Subsystem.
\item Test authentication of valid user email and password combination gains access to administration area.
\item Test authentication of invalid user email address that does not gain access to administration area.
\item Test whether logging out destroys user session and redirects to login subsystem.
\end{itemize}

\vspace{2 mm}
\textbf{User Management Subsystem Test Plan :}

\begin{itemize}
\item Test whether all authenticated users are listed.
\item Test ability to create a user for further functional tests.
\item Test ability to update user password.
\item Test whether updating a user account to inactive denies access to administration area.
\item Test ability to delete a user.
\end{itemize}

\vspace{2 mm}
\textbf{Page Management Subsystem Test Plan :}

\begin{itemize}
\item Test whether all pages are listed.
\item Test ability to create a new page for further functional tests.
\item Test ability to update page name.
\item Test ability to update page title.
\item Test ability to update page content.
\item Test ability to delete page.
\end{itemize}

\vspace{2 mm}
\textbf{\Large Non-functional Requirements Testing}
\vspace{5 mm}

\textbf{PHP Unit Testing :}

\begin{itemize}
\item PHPUnit will be used for all PHP unit tests.
\end{itemize}

\vspace{2 mm}
\textbf{Javascript Unit Testing :}

\begin{itemize}
\item QUnit will be used for all Javascript unit tests.
\end{itemize}

\vspace{2 mm}
\textbf{HTML Testing :}

\begin{itemize}
\item All HTML will be validated with an industry standard HTML validator.
\end{itemize}

\vspace{2 mm}
\textbf{CSS Testing :}

\begin{itemize}
\item All CSS will be validated with an industry standard CSS validator.
\end{itemize}




\end{document}
