\documentclass[11pt]{article}

\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}



\begin{document}

\title{Problem Statement} 
\author{Team: The Outsiders\\ \\ Kirk Montour (montour)\\ Syed Gardezi (gardezsh)}
\date{\today}
  
\maketitle

\pagebreak

\tableofcontents

\pagebreak

\section{Content Management System Motivation}
Companies spend lots of money maintaining their websites. Companies have to hire a full-time web administrator, or have to outsource their web administration which is very expensive. There must be a more cost-effective way to maintain a web presence. A company could save a lot of money if they could just update their websites themselves. A Content Management System is the perfect software to rectify the situation because a Content Management System allows non-technical people to update their websites themselves. If you can use a Word Processor, you can update a Content Management System. If you can update a Content Management System, you can maintain your own website. If you can maintain your own website, you can save lots of money.

\section{Detailed Objectives}

\begin{itemize}
  \item Our team would like to facilitate day to day website maintenance for non-technical users
  \item Facilitating website maintenance for non-technical users reduces website maintenance costs
  \item Non-technical users will be restricted to creating static web pages
\end{itemize}

\section{Assumptions}

\begin{itemize}
  \item Users of Content Management System have no experience with HTML
  \item Users of Content Management System have no experience with javascript
  \item Users of CMS have no experience with CSS
  \item Users of CMS have no experience with PHP
  \item Users of CMS have some experience with a word processor
  \item Users of CMS have web surfing experience
  \item Users of CMS have experience navigating a website
  \item Users of CMS have some experience with registering with websites
  \item Users of CMS have some experience with filling out web forms
\end{itemize}


\section{Constraints}
\begin{itemize}
  \item Our project is constrained to static pages, cannot expect non-technical users to create dynamic database driven pages
  \item Non-technical users will have to choose one of the pre-installed themes for their website, cannot expect non-technical users to create a theme
\end{itemize}

\section{Challenges}
\begin{itemize}
  \item Seeing contingencies for non-technical users ahead of time
  \item Adhering to the MVC paradigm
  \item Designing and co-ordinating all the different modules
  \item Designing the database and database components
  \item Designing a user-friendly UI
  \item Researching different technologies
\end{itemize}


\end{document}